---
title: "Read me"
author: "Liz Bowman"
date: "10/26/2016"
output: html_document
---

The folders here contain R scripts and data files for the article "Distributions of ectomycorrhizal and foliar endophytic fungal communities associated with Pinus ponderosa along a spatially constrained elevation gradient" written by Elizabeth A. Bowman and A.
Elizabeth Arnold.

A. Elizabeth Arnold is the author for correspondence on this article. 
Address: 1140 E. South Campus Drive
Forbes 303
School of Plant Sciences
The University of Arizona
Tucson, AZ 85721 USA. 
Email: arnold@ag.arizona.edu

Elizabeth A. Bowman wrote all scripts for data analysis.
Email: eabowman@email.arizona.edu

------------------------------------------------------------------------------------------

Explanation of folders:
1. The data folder contains all data files used in the R script for analyses with
explanations of columns.
2. The figure folder is an output folder where figures generated in the R script will be
output.
3. The results folder is an output folder for results tables generated in the R script.
4. The script folder contains all scripts organized by type of analysis.

Each of these folders contains a 'Read me' file with further explanations.

------------------------------------------------------------------------------------------

The following code will run each analysis and output figures and result tables to their
appropriate folders. All analyses below—with the exception of the analyses listed under 'Analyses using OTU-informed morphotypes' are run using sequenced root tip data (see manuscript for explanation of sequenced root tips versus OTU-informed morphotypes)

# Load file paths

```{r file paths}
#--file path to data directory
dat.dir <- 'data/'
fig.dir <- 'figures/'
res.dir <- 'results/'
script.dir <- 'script/'
```

# Load packages  

If you need to install packages, open 'Load_packages.R' and uncomment 'install.packages'
before running. 

```{r libraries}
source(paste0(script.dir, "Load_packages.R"))
```

# Abundance analyses  

```{r abundance}
source(paste0(script.dir, "Abundance_analyses.R"))
```

# Environmental analyses  

```{r environmental}
source(paste0(script.dir, "Environmental_analyses.R"))
```

# Diversity analyses  

```{r diversity}
source(paste0(script.dir, "Diversity_analyses.R"))
```

# Species accumulation curves analyses  

```{r sp accumulation}
source(paste0(script.dir, "Species_accumulation_curves.R"))
```

# Community composition analyses 

Within the 'Bowman and Arnold - American Journal of Botany 2016 - Ordination analyses.R' script there is code to remove singletons, just uncomment them (remove # sign). The code as it is run has outliers removed, but you can include them by commenting out those lines (add # sign before code). All code is commented with explanations of what their function is.

```{r community}
source(paste0(script.dir, "Ordination_analyses.R"))
```

# Taxonomic analyses 

```{r taxonomy}
source(paste0(script.dir, "Taxonomic_analyses.R"))
```

# Indicator species analyses 

```{r indicator}
source(paste0(script.dir, "Indicator_species_analyses.R"))
```


# Topographical analyses

```{r topography}
source(paste0(script.dir, "Topographical_analyses.R"))
```


# Analyses using OTU-informed morphotypes
NMDS, ANOSIM, and PERANOVA analyses using OTU-informed morphotypes is executed in the same script as above ('Ordination_analyses.R')

Indicator species analyses using OTU-informed morphotypes is executed in the same script as above ('Indicator_species_analyses.R')

### Diversity
```{r OTU-informed morphotypes: Diversity}
source(paste0(script.dir, "Diversity_analyses_based_on_EMmorphotype_data.R"))
```

### Species accumulation curves
```{r OTU-informed morphotypes: Species accumulation curves}
source(paste0(script.dir, "Species_accumulation_curves_based_on_EMmorphotype_data.R"))
```

### Taxonomy
```{r OTU-informed morphotypes: Taxonomy}
source(paste0(script.dir, "Taxonomic_analyses_based_on_EMmorphotype_data.R"))
```
